---
title: "Homework 6"
author: "Suning Zhao"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(mgcv)


devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))

set.seed(1)
```


```{r load_libraries}
library(tidyverse)
library(modelr)
library(mgcv)
library(purrr)
```

### Problem 1

To obtain a distribution for $\hat{r}^2$, we'll follow basically the same procedure we used for regression coefficients: draw bootstrap samples; the a model to each; extract the value I'm concerned with; and summarize. Here, we'll use `modelr::bootstrap` to draw the samples and `broom::glance` to produce `r.squared` values. 

```{r weather_df, cache = TRUE}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::glance)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  ggplot(aes(x = r.squared)) + geom_density()
```

In this example, the $\hat{r}^2$ value is high, and the upper bound at 1 may be a cause for the generally skewed shape of the distribution. If we wanted to construct a confidence interval for $R^2$, we could take the 2.5% and 97.5% quantiles of the estimates across bootstrap samples. However, because the shape isn't symmetric, using the mean +/- 1.96 times the standard error probably wouldn't work well.

We can produce a distribution for $\log(\beta_0 * \beta1)$ using a similar approach, with a bit more wrangling before we make our plot.

```{r}
weather_df %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  select(id = `.id`, term, estimate) %>% 
  pivot_wider(
    names_from = term, 
    values_from = estimate) %>% 
  rename(beta0 = `(Intercept)`, beta1 = tmin) %>% 
  mutate(log_b0b1 = log(beta0 * beta1)) %>% 
  ggplot(aes(x = log_b0b1)) + geom_density()
```

As with $r^2$, this distribution is somewhat skewed and has some outliers. 

The point of this is not to say you should always use the bootstrap -- it's possible to establish "large sample" distributions for strange parameters / values / summaries in a lot of cases, and those are great to have. But it is helpful to know that there's a way to do inference even in tough cases. 

### Problem 2

#### Loading the dataset
* First, I used `read_csv` to read the original dataset and used `janitor::clean_names` to clean the title.
* Then, I used `mutate` to create `city_state` variable and a binary variable indicating whether the homicide is solved called `homicides_status`, and translate `victim_age` as a numeric vector.
* Lastly, I used `filter` to omit some cities and limit the analysis for whom `victim_race` is `white` or `black`.
```{r}
homicides_raw_df = 
  read_csv("data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    city_state = str_c(city,state, sep = ","),
    homicides_status = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age)
  ) %>% 
  filter(
    !city_state %in% c("Dallas,TX", "Phoneix,AZ", "Kansas City,MO", "Tulsa,AL"),
    victim_race %in% c("White", "Black")
    )
```

#### Create a GLM model for Baltimore,MD
* First, I used `glm` function to fit a logistic regression model with `homicides_status` as outcome and `victim_age`, `victim_sex` and `victim_race` as predictors.
* Then, I applied `broom::tidy` to this object.
* In order to estimate the odds ratio and confidence interval, I used `exp` to translate the log odds ratio to odds ratio, and calculate the 95% confidence interval by multiple 1.96.
* Finally, I used `filter` to only compare male victims to female victims keeping all other variables fixed.
```{r}
glm_baltimore = 
  homicides_raw_df %>%
  filter(city_state == "Baltimore,MD") %>% 
  glm(homicides_status ~ victim_age + victim_sex + victim_race, data = ., family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate - 1.96 * std.error),
         CI_upper = exp(estimate + 1.96 * std.error)) %>%
  select(term, OR, CI_lower, CI_upper) %>% 
  filter(term == "victim_sexMale")

glm_baltimore %>% 
knitr::kable(digits = 3)
```

#### Create a GLM model for each cities
* In order to create a GLM model for each cities, firstly, I used `nest` to nest the datas excluding `city_state`.
* Then, I used `mutate` and `map` to generalize logistic regression model for each city and marked the results as `results`.
* After that, I `unnest` the dataframe and used `mutate` to translate log odds ratio and calculate the confidence interval.
* Finally, I used `filter` to only compare male victims to female victims keeping all other variables fixed.
```{r}
glm_homicides_df = 
  homicides_raw_df %>%
  nest(data = -city_state) %>% 
  mutate(
    models = map(data, ~glm(homicides_status ~ victim_age + victim_sex + victim_race, data = ., family = binomial())),
    results = map(models, broom::tidy)
    ) %>% 
  select(-data, -models) %>% 
  unnest(results) %>% 
  mutate(OR = exp(estimate),
         CI_lower = exp(estimate - 1.96 * std.error),
         CI_upper = exp(estimate + 1.96 * std.error)) %>%
  filter(term == "victim_sexMale") %>% 
  select(city_state, OR, CI_lower, CI_upper)

glm_homicides_df %>% 
  knitr::kable(digits = 3)
```

#### Create a plot that shows the estimated ORs and CIs for each city
* First, I reordered the cities according to OR using `fct_reorder`.
* Then, I created a plot use `ggplot`, `geom_point` and `geom_line`.
```{r}
glm_homicides_df %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>%
  ggplot(aes(x = city_state, y = OR))+
  geom_point()+
  geom_errorbar(mapping = aes(ymin = CI_lower, ymax = CI_upper))+
  labs( x = "City, State",  y = "Odds Ratio", title = "Estimated ORs and CIs of Solving Homicides Comparing Male to Female Victims") + 
  theme(plot.title = element_text(hjust = 0.5)) + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

* According to the plot, we can know that the estimated odds ratio of solving homicides between male and female victims lies in between 0 and 2.
* For 50 cities, only 4 cities are with odds ratio higher than 1, which suggests that male victims has a larger chance to have a solving homicides. Those cities are Nashville,TN, Fresno,CA, Stockton,CA, and Albuquerque,NM. 
* `Fresno,CA`, `Stockton,CA`, and `Albuquerque,NM`have wider confidence intervals than others, with higher standard errors. Those may be because of a small sample in those cities or some outliers.

### Problem 3

#### Load and clean the data for regression analysis
* I used `read_csv` to read the original file in dataset, and then used `mutate` to translate parts of numeric variables into factors.
* Then I tested the missing data using `sum`. It showed that there was no missing value in the dataset.
```{r}
birth_weight_df = 
  read_csv("data/birthweight.csv") %>% 
  mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace),
  )

sum(is.na(birth_weight_df))
```

#### Create a regression model for birthweight
* I used `step` function to create the model using stepwise method.
```{r}
my_model <- lm(bwt ~.,
               data =birth_weight_df)
step(my_model, direction = "both", trace  = FALSE)

my_model %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(
    digits = 3,
    col.names = c("Term", "Estimate", "P-value")
  )
```

* The result shows that `babysex2`, `bhead`, `blength`, `delwt`, `fincome`, `gaweeks`, `mheight`, `mrace`, `parity`,`ppwt` and `smoken` can be the predictors.
* Then, I created a plot to illustrate the relationship between residuals and fitted values, using `add_predictions` and `add_residuals`.
```{r}
birth_weight_df %>% 
  add_predictions(my_model) %>% 
  add_residuals(my_model) %>% 
  ggplot(aes(x = pred, y = resid)) +
  geom_point(alpha = 0.5) +
  geom_smooth(formula = 'y ~ x',method = "lm", se = FALSE) +
  labs(title = "Fitted Values vs. Residuals",
       x = "Fitted Values", 
       y = "Residuals") +
  theme(plot.title = element_text(hjust = 0.5))
```

* From the graph we can know that most of residuals are lying around 0 when fitted value is between 2000 to 4000. 
* Some outliers should also be pointed out when fitted values are too small. The largest bias is around 2000. This might be due to the data collection step.

#### Compare my model to two others

* Created the models first.
```{r}
model_1 = lm(bwt ~ blength + gaweeks, data = birth_weight_df)

model_2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + bhead*babysex + blength*babysex + bhead*blength*babysex,
               data = birth_weight_df)

model_1 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(
    digits = 3,
    col.names = c("Term", "Estimate", "P-value")
  )

model_2 %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  knitr::kable(
    digits = 3,
    col.names = c("Term", "Estimate", "P-value")
  )
```
* From the results we can know that model 1 is with only two predictors, while model 2 is with 7 predictors, including some interactions. Because model 2 is much more complicated, it might be with a better prediction but we should check with the prediction error.

#### Check the prediction error between three models
* First, I used `crossv_mc` and `map` to generate train dataset and test dataset.
* Then I generated models in each dataset and calculated the rmse.
* Last, I created a plot for RMSE among three models.
```{r}
cv_df = 
  crossv_mc(birth_weight_df, 100) %>% 
  mutate(train = map(train, as_tibble),
    test = map(test, as_tibble))%>% 
  mutate(
    model_1  = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_2  = map(train, ~lm(bwt ~ bhead * blength * babysex, data = .x)),
    my_model  = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + fincome + gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x ))) %>% 
  mutate(
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2  = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
  select(starts_with("rmse")) %>%
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>%
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + 
  geom_violin() +
  labs(title = "Comparison of the Cross-Validated Prediction Error", 
       x = "Models", 
       y = "Root Mean Square Error (RMSE)")   
```

* From the graph we can know that my model is with the smallest RMSE, which means that it can predict the birthweight best.
* For two models, model 2 is better than model 1, with a smaller RMSE. The RMSE for my model is not with a huge difference compared with model 2.
